Stock enhancement undermines community stability

### 2022-02-04 rmd/supporting_info.Rmd
Update supporting_info.Rmd

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$]and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll a concentration [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. We extracted annual data of chlorophyll a concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth. Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll a concentration; averaged for 2002-2019). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.

@@

Distribution of environmental variables in the protected watershed. Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level.

>>>>

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth. Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.

@@

Distribution of environmental variables in the protected watershed. Note that the number of fish released and ocean productivity (chlorophyll *a*) are measured at the watershed level while others are measured at the site level.
